Investigating the Applications and Limits of Single Asymmetric Particle Light Scattering using Limited Detection Schemes

### 2022-11-14 Manuscript.tex
more work on cleaning up text

\begin{align}
	\label{eq:scale}
	y_k(\hat{\bf n}_i,\ \theta_k) = 
	 \frac{\left[I(\hat{\bf n}_i, \ \theta_k)- \langle I(\hat{\bf n}, \ \theta_k) \rangle \right]} 
	{\langle I^2(\hat{\bf n},\ \theta_k) \rangle -\langle I(\hat{\bf n}, \ \theta_k)\rangle^2}
\end{align}

Where the denominator is simply the standard deviation for our values of $I(\hat{\bf n}, \theta_k)$. The dimer's \emph{actual}  instantaneous scattered intensity based on the real instantaneous orientation $\bar{\bf s}$  is similarly scaled using \eqref{eq:scale} to give $y(\bar{\bf s},\ \theta_k)$. See Table's A.1 and A.2 for numerical values of our reference orientation, raw intensities, and scaled signals. In practice $y(\bar{\bf s}\, \theta_k)$ will have an inherent amount of uncertainty in our measurement due to noise from our detector. We compare our instantaneous signal to our reference signal by assuming that the measurement uncertainty for each detection fibre is Gaussian and is centred about $y_k(\bar{\bf s})$ Combining all three detection angles provides us with the conditional probability that, should the dimer be in orientation $\hat{\bf n}_i$, it would produce a signal $y(\bar{\bf s})$:

\begin{align}
	\label{eq:conditional}
	p_i(y(\bar{\bf s})\parallel\hat{\bf n}_i) = \Pi^3_{k=1}
	(2\pi\sigma_k^2)^{-1/2} 
	e^{-(y_{k}(\hat{\bf n}_i)-y_{k}(\bar{\bf s}))^2/2\sigma_k^2}
\end{align}

Where $\sigma_k$ is the average error in the detected signal from our dimer $y_k(\bar{\bf s})$. We left this as a tuneable variable to measure how the influence of experimental error would effect our predictive model. The signal error was simulated in our model by stochastically adjusting our values of $y_k(\bar{\bf s})$.

\begin{eqnarray*}
	\sigma_k = \epsilon\bar{y}(\hat{\bf n}_k) \\
	\Rightarrow y(\bar{\bf s}_k) = y(\bar{\bf s})_k \pm n\sigma_k \\ 
	n \in \mathbb{R}, n\in[0,1]
\end{eqnarray*}

Where $\epsilon$ is the percent error expected from our detection fibres. Equation~\eqref{eq:conditional} assigns a probability to each reference orientation based on how similar the 'reference orientation signal' $y_{k}(\hat{\bf n}_i)$ is to the actual signal $y_{k}(\bar{\bf s})$ generated by the dimer in its real orientation $\bar{\bf s}$. However, if our values of $y_k(\hat{\bf n}_i)$ are similar to one another the probability distribution from equation~\ref{eq:conditional} will therefore assign similar probability for multiple reference orientations. Bayesian inference allows one to update a probability distribution by accounting for information known prior to making a measurement. We apply this by accounting for our distribution of reference orientations and instantaneous signals.

\begin{align}
	\label{eq:bayes}
	p_i(\hat{\bf n}\parallel y(\bar{\bf s}))&= \frac{p_i(y(\bar{\bf s})\parallel\hat{\bf n})p_i(\hat{\bf n})}{p(y)}
\end{align}

Where $p_i(\hat{\bf n})$ and $p(y)$ are our estimations of the prior distributions of particle orientations and instantaneous signals respectively. The former can be estimated by some Boltzmann distribution based on how far apart reference orientations are in physical space, covered in Section~\ref{sec:2.3}. The latter prior $p(y)$ is the probability of our dimer producing a signal $y_k(\bar{\bf s})$ that falls with our distribution of reference signals $y_k(\hat{\bf n})$. This is given by taking the discrete integral over collection of reference orientations.

\begin{align}
	p(y) = \sum\limits_{i=1}^{30} p_i(y(\bar{\bf s})\parallel\hat{\bf n})p_i(\hat{\bf n})
 \end{align}

The implementation of \eqref{eq:bayes} improves our estimate by suppressing reference orientations that are far away from our dimer's orientation vector in physical space. In order to evaluate the accuracy of our model we tested it using our Brownian simulation of the dimer, see Section~\ref{sec:2.1}.

\subsection{Testing our Model}
\label{sec:2.3}
Using our simulation from Section~\ref{sec:2.1} we calculated the instantaneous signal from our dimer at each time step using MSTM.  We applied \eqref{eq:bayes} - covered in Section~\ref{sec:2.2} - and the reference orientation with the highest probability is taken as our estimation of the dimer's instantaneous orientation. The priori of reference orientations $p_i(\hat{\bf n})$ is defined at each time step by accounting for the physical distance between our previous estimation $\hat{\bf n}_{i, \ t - \Delta t}$ and each reference orientation $\hat{\bf n}$

\begin{align}
	r_i(t, \hat{\bf n}_i)= \frac{1}{2}((\hat{\bf n}_{i,\ t} \cdot \hat{\bf n}_{t-\Delta t})-1) \\
	p_i(\hat{\bf n})= \frac{e^{\beta (r_i(t,\hat{\bf n}_i)-1)}}
	{\Sigma_{j=1}^{30}e^{\beta(r_j(t, \hat{\bf n}_i)-1)}}
\end{align}
where $\beta$ is a weighting factor that controls the significance of
our priori estimate. The simulation data from Section~\ref{sec:2.1}
was used to check if the estimation was correct by comparing the
estimate provided by \eqref{eq:bayes} to the reference orientation
closest to the instantaneous orientation, denoted as
$\hat{\bf n}_{best}$.  To measure the error in the model's estimate the
distribution's of $p(\hat{\bf n}\parallel y(\bar{\bf s}))$ and an ideal
result, $p_ideal$, were compared. An ideal distribution is one that is
0 for every $\hat{\bf n}$ apart from the correct result.
\begin{align}
	p_{ideal} = 
	\begin{cases}
		1 & \text{when $\hat{\bf n}_i$ = $\hat{\bf n}_{best}$}\\
		0 & \text{anywhere else}
	\end{cases}
\end{align}
The distribution from \eqref{eq:bayes} will assign some non-zero probability to every reference orientation.  The model's error was measured by calculating the Kullback-Leibler ($K_l$) divergence between the two distributions

\begin{align}
	K_{l, \#}(p_i(\hat{\bf n}\parallel y_k(\bar{\bf s})) &\parallel p_{ideal}) =\nonumber \\
	&p_{ideal}\ln \left[\frac{p_{ideal}}{p(\hat{\bf n}_{best}\parallel y(\bar{\bf s}))}
	\right]
\end{align}
where a more negative value of $K_l$ indicates a poorer estimation of
the dimer's instantaneous orientation. By summing the divergence of
each measurement across the entire simulation we get an evaluation of
how well the model performed in estimating the dimer's orientation. To
compare between different iterations of our model the we compare our
result of $K_l$ to a worst case scenario and evaluate how much it
improves upon this, denoted as $F(K_l)$:
\begin{align}
	K_{l, \ total} &= \sum\limits_{\# =1}^{timesteps} K_{l,\#} \\
	K_{l, \ worst} &= -\sum\limits_{\#=1}^{timesteps} \ln \left[\frac{1}{1/30} \right] \\
	F(K_l) &= \frac{K_{l,\ worst}}{K_{l, \ total}}
\end{align}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Optimization of parameters}
\label{sec:2.4}
The signal error $\epsilon$ and the weighting factor $\beta$ are known quantities whose influence can be measured directly. However, our choice of angles and how they correlate with $F(K_l)$ is not easily understood Evaluating every possible configuration manually is inefficient, therefore we utilised Ultra-nest to apply a Monte Carlo simulation to our model. Ultra-nest is a sophisticated python package for fitting models with complex parameter correlations \cite{Buchner2016Ultranest}. Ultra-nest implements a variation of Monte Carlo integration, nested-sampling, where a likelihood contour is used to update a group of live points chosen from the prior estimation ($0^{\circ} \leq \theta_k \leq 180^{\circ}$).

The Ultra-nest software was used to create a set of live points of different choices of $\theta_1, \ \theta_2, \ \& \ \theta_3$, with each point being evaluated by its improvement factor ($F(K_l)$). After evaluating every live point, the worst results are removed and new live points are created based on the information provided by the previous live points. If there is a correlation between the choice of angles and $F(K_l)$ then the live points should congregate around a single (or multiple) choice of angles that will maximise $F(K_l)$ and therefore minimise the error between our estimate and instantaneous orientation.

\section{Results $\&$ Discussion}
\label{sec:Discussion}
\subsection{Asymmetric dimer dynamics}
\label{sec:3.1}
The Brownian OT software was used to simulate the motion of a trapped dimer ($a_1=1\mu m, a_2=0.5\mu m$) over the first 10 seconds of entering the optical trap. The initial orientation was assumed as strictly vertical (in line with the beam propagation direction). The dimer's position orientation was recorded every $10 \mu s$ for using as a test dataset for our model.

@@

As can be seen from Figure~\ref{fig:motion}, the dimer undergoes a full $180^{\circ}$ rotation upon entering the trap. Typically horizontal alignment of a dimer is unstable and will result in the particle rotating to align along its vertical axis. It is interesting to note that the dimer is furthest from the trap centre as it goes into a horizontal orientation before drawing closer again as it inverts completely. Further simulations of differently sized dimers showed similar results, but only when $a_1 \geq 2a_2$. Dimers with more symmetrical size ratios immediately aligned into a fixed vertical position. 
In Vigilante's work with dimers \cite{Vigilante2020Brownian_OT} simulations of trapped symmetrical dimers was investigated; their findings showed that the optical torque on the dimer goes to zero while aligned vertically and is at its maximum in a horizontal alignment. Therefore, the inversion of an asymmetric dimer suggests that if the size difference is significant the optical torque goes is minimal for a dimer in both horizontal and vertical orientations. Once we have our experimental set up complete we can confirm this by trapping an asymmetric dimer and monitoring its orientation. The data from \figurename{ 2a} was used to test the efficacy of our predictive model. To visualise how well our model tracks the dimer's orientation we plot the radial distance between our model's prediction and the true orientation, and between the best possible orientation and the true orientation. For a perfect estimation these two plots should overlap, while we cannot achieve an exact estimation we can optimise it by adjusting the expected signal error and weighting factor.

\subsection{Impact of signal error on model predictions}
\label{sec:3.2}
A key assumption of equation~\ref{eq:conditional} is that we assume our detected light signal will inherently have some degree of noise. This is the central premise that allows us to form equation~\eqref{eq:conditional}, understanding the limits of acceptable signal error is necessary for implementing this to experimental work.
To this end we ran our model while varying the value of $\epsilon$. \figurename{ 3} shows the model's performance with a selection of angles $15^{\circ},\ 55^{\circ}, \ \& \ 90^{\circ}$ and $\beta$ set at 1. The dotted line indicates the minimum radian distance ($0.137$ radians) between two neighbouring reference orientations, if we are under this line then we know our model is just off from selecting the correct orientation

@@

We have developed a model for interpreting the dynamics of a trapped particle based purely on the light scattering pattern. In theory the model can be applied to any characteristic that impacts the light scattering pattern produced by the trapped entity. The MSTM package is flexible in calculating the light scattering for a variety of micro-particles; so long as there is a distinguishable difference in the light scattering pattern we can apply this method to characterise the particle to some degree of accuracy. This has potential to be applied to characterise particle size and shape that are changing while in the optical trap. The authors would like to acknowledge and thank the support for this research from the funding provided by the Leverhulme Trust.\\

@@

\newpage
\appendix
\onecolumn
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Appendix}
\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}
\label{sec:App1}
\begin{table}[h]
	\label{tab:A1}
	\begin{center}
		\caption{Reference Orientations vector components$^*$}
		\begin{tabular}{|c|c|c|c|}
			\hline\hline
			Reference Orientation i & $\hat{\bf n}_{i,\ x}$ &  $\hat{\bf n}_{i,\ y}$ &  $\hat{\bf n}_{i,\ z}$ \\
			\hline
			$1$ & $ 0.29588$ &  $ 0.29588$ & $ 0.90825$ \\
			$2$ & $ 0.90825$ &  $ 0.29588$ & $ 0.29588$ \\
			$3$ & $ 0.29588$ &  $ 0.90825$ & $ 0.29588$ \\
			$4$ & $1.0000$ &  $0.00000$ & $0.00000$ \\
			$5$ & $0.00000$ &  $1.0000$ & $0.00000$ \\
			$6$ & $0.00000$ &  $0.00000$ & $1.0000$ \\
			$7$ & $ 0.29588$ &  $ 0.29588$ & $-0.90825$ \\
			$8$ & $ 0.90825$ &  $ 0.29588$ & $-0.29588$ \\
			$9$ & $ 0.29588$ &  $ 0.90825$ & $-0.29588$ \\
			$10$ & $0.00000$ &  $0.00000$ & $-1.0000$ \\
			$11$ & $ 0.29588$ &  $-0.29588$ & $ 0.90825$ \\
			$12$ & $ 0.90825$ &  $-0.29588$ & $ 0.29588$ \\
			$13$ & $ 0.29588$ &  $-0.90825$ & $ 0.29588$ \\
			$14$ & $0.00000$ &  $-1.0000$ & $0.00000$ \\
			$15$ & $ 0.29588$ &  $-0.29588$ & $-0.90825$ \\
			$16$ & $ 0.90825$ &  $-0.29588$ & $-0.29588$ \\
			$17$ & $ 0.29588$ &  $-0.90825$ & $-0.29588$ \\
			$18$ & $-0.29588$ &  $ 0.29588$ & $ 0.90825$ \\
			$19$ & $-0.90825$ &  $ 0.29588$ & $ 0.29588$ \\
			$20$ & $-0.29588$ &  $ 0.90825$ & $ 0.29588$ \\
			$21$ & $-1.0000$ &  $0.00000$ & $0.00000$ \\
			$22$ & $-0.29588$ &  $ 0.29588$ & $-0.90825$ \\
			$23$ & $-0.90825$ &  $ 0.29588$ & $-0.29588$ \\
			$24$ & $-0.29588$ &  $ 0.90825$ & $-0.29588$ \\
			$25$ & $-0.29588$ &  $-0.29588$ & $ 0.90825$ \\
			$26$ & $-0.90825$ &  $-0.29588$ & $ 0.29588$ \\
			$27$ & $-0.29588$ &  $-0.90825$ & $ 0.29588$ \\
			$28$ & $-0.29588$ &  $-0.29588$ & $-0.90825$ \\
			$28$ & $-0.90825$ &  $-0.29588$ & $-0.29588$ \\
			$30$ & $-0.29588$ &  $-0.90825$ & $-0.29588$ \\
			\hline\hline
			\multicolumn{4}{l}{\small *Orientation vector points from centre of sphere 1 to centre of sphere 2.} \\
		\end{tabular}
	\end{center}
\end{table}

>>>>

\begin{align}
	\label{eq:scale}
	y_k(\hat{\bf n}_i,\ \theta_k) = 
	 \frac{\left[I(\hat{\bf n}_i, \ \theta_k)- \langle I(\hat{\bf n}, \ \theta_k) \rangle \right]} 
	{\langle I^2(\hat{\bf n},\ \theta_k) \rangle -\langle I(\hat{\bf n}, \ \theta_k)\rangle^2}
\end{align}
where the denominator is simply the standard deviation for our values
of $I(\hat{\bf n}, \theta_k)$.  The dimer's \emph{actual}
instantaneous scattered intensity based on the real instantaneous
orientation $\bar{\bf s}$ is similarly scaled using \eqref{eq:scale}
to give $y(\bar{\bf s},\ \theta_k)$.  See Tables A.1 and \ref{tab:A2}
for numerical values of our reference orientation, raw intensities,
and scaled signals.  In practice, $y(\bar{\bf s}\, \theta_k)$ will
have an inherent amount of uncertainty in our measurement due to noise
from our detector.  We compare our instantaneous signal to our
reference signal by assuming that the measurement uncertainty for each
detection fibre is Gaussian and is centred about $y_k(\bar{\bf s})$
Combining all three detection angles provides us with the conditional
probability that, should the dimer be in orientation $\hat{\bf n}_i$,
it would produce a signal $y(\bar{\bf s})$:
\begin{align}
	\label{eq:conditional}
	p_i(y(\bar{\bf s})|\hat{\bf n}_i) = \Pi^3_{k=1}
	(2\pi\sigma_k^2)^{-1/2} 
	e^{-(y_{k}(\hat{\bf n}_i)-y_{k}(\bar{\bf s}))^2/2\sigma_k^2}
\end{align}
where $\sigma_k$ is the average error in the detected signal from our
dimer $y_k(\bar{\bf s})$.  We left this as a tuneable variable to
measure how the influence of experimental error would effect our
predictive model.  The signal error was simulated in our model by
stochastically adjusting our values of $y_k(\bar{\bf s})$.
\begin{eqnarray*}
  \sigma_k
  &= \epsilon\bar{y}(\hat{\bf n}_k)
  \\
  \Rightarrow y(\bar{\bf s}_k) &= y(\bar{\bf s})_k \pm n\sigma_k
  \\ 
n \in \mathbb{R}, n\in[0,1]
\end{eqnarray*} 
where $\epsilon$ is the percent error expected from our detection
fibres.  Equation~\eqref{eq:conditional} assigns a probability to each
reference orientation based on how similar the 'reference orientation
signal' $y_{k}(\hat{\bf n}_i)$ is to the actual signal
$y_{k}(\bar{\bf s})$ generated by the dimer in its real orientation
$\bar{\bf s}$.  However, if our values of $y_k(\hat{\bf n}_i)$ are
similar to one another the probability distribution from
Eq.~\eqref{eq:conditional} will therefore assign similar
probability for multiple reference orientations. Bayesian inference
allows one to update a probability distribution by accounting for
information known prior to making a measurement.  We apply this by
accounting for our distribution of reference orientations and
instantaneous signals.
\begin{align}
  \label{eq:bayes}
  p_i(\hat{\bf n}| y(\bar{\bf s}))
  &=
    \frac{p_i(y(\bar{\bf s})|\hat{\bf n})p_i(\hat{\bf n})}{p(y)}
\end{align}
where $p_i(\hat{\bf n})$ and $p(y)$ are our estimations of the prior
distributions of particle orientations and instantaneous signals
respectively.  The former can be estimated by some Boltzmann
distribution based on how far apart reference orientations are in
physical space, covered in Section~\ref{sec:2.3}.  The latter prior
$p(y)$ is the probability of our dimer producing a signal
$y_k(\bar{\bf s})$ that falls with our distribution of reference
signals $y_k(\hat{\bf n})$.  This is given by taking the discrete
integral over collection of reference orientations.
\begin{align}
  p(y)
  =
  \sum_{i=1}^{30} p_i(y(\bar{\bf s})|\hat{\bf n})p_i(\hat{\bf n})
\end{align}
The implementation of Eq.~\eqref{eq:bayes} improves our estimate by
suppressing reference orientations that are far away from our dimer's
orientation vector in physical space.  In order to evaluate the
accuracy of our method, we tested it using a Brownian dynamics
simulation of the dimer (see Section~\ref{sec:2.1}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Testing the Model}
\label{sec:2.3}

Using our simulation from Section~\ref{sec:2.1} we calculated the
instantaneous signal from our dimer at each time step using MSTM.  We
applied Eq.~\eqref{eq:bayes} --- covered in Section~\ref{sec:2.2} ---
and the reference orientation with the highest probability is taken as
our estimation of the dimer's instantaneous orientation.  The prior of
the reference orientations $p_i(\hat{\bf n})$ is defined at each time
step by accounting for the physical distance between our previous
estimation $\hat{\bf n}_{i, \ t - \Delta t}$ and each reference
orientation $\hat{\bf n}$
\begin{align}
  r_i(t, \hat{\bf n}_i)
  &= \frac{1}{2}((\hat{\bf n}_{i,\ t} \cdot \hat{\bf n}_{t-\Delta t})-1)
  \\
  p_i(\hat{\bf n})
  &= \frac{e^{\beta (r_i(t,\hat{\bf n}_i)-1)}}
{\sum_{j=1}^{30}e^{\beta(r_j(t, \hat{\bf n}_i)-1)}}
\end{align}
where $\beta$ is a weighting factor that controls the significance of
our priori estimate.  The simulation data from Section~\ref{sec:2.1}
was used to check if the estimation was correct by comparing the
estimate provided by Eq.~\eqref{eq:bayes} to the reference orientation
closest to the instantaneous orientation, denoted as
$\hat{\bf n}_{best}$.  To measure the error in the model's estimate
the distribution's of $p(\hat{\bf n}| y(\bar{\bf s}))$ and an
ideal result, $p_ideal$, were compared.  An ideal distribution is one
that is 0 for every $\hat{\bf n}$ apart from the correct result.
\begin{align}
p_{ideal} = 
\begin{cases}
	1 & \text{when $\hat{\bf n}_i$ = $\hat{\bf n}_{best}$}\\
	0 & \text{anywhere else}
\end{cases}
\end{align}
The distribution from Eq.~\eqref{eq:bayes} will assign some non-zero
probability to every reference orientation.  The model's error was
measured by calculating the Kullback-Leibler divergence $K_l$ between
the two distributions
\begin{align}
  K_{l, \#}(p_i(\hat{\bf n}| y_k(\bar{\bf s})) &\parallel p_{ideal}) =\nonumber
  \\
&p_{ideal}\ln \left[\frac{p_{ideal}}{p(\hat{\bf n}_{best}| y(\bar{\bf s}))}
\right]
\end{align}
where a more negative value of $K_l$ indicates a poorer estimation of
the dimer's instantaneous orientation.  By summing the divergence of
each measurement across the entire simulation we get an evaluation of
how well the model performed in estimating the dimer's orientation.
To compare between different iterations of our model the we compare
our result of $K_l$ to a worst case scenario and evaluate how much it
improves upon this, denoted as $F(K_l)$:
\begin{align}
	K_{l, \ total} &= \sum\limits_{\# =1}^{timesteps} K_{l,\#} \\
	K_{l, \ worst} &= -\sum\limits_{\#=1}^{timesteps} \ln \left[\frac{1}{1/30} \right] \\
	F(K_l) &= \frac{K_{l,\ worst}}{K_{l, \ total}}
\end{align}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Optimization of parameters}
\label{sec:2.4}

The signal error $\epsilon$ and the weighting factor $\beta$ are known
quantities whose influence can be measured directly; however, our
choice of angles and how they correlate with $F(K_l)$ is not easily
understood Evaluating every possible configuration manually is
inefficient, therefore we utilised Ultra-nest to apply a Monte Carlo
simulation to our model. Ultra-nest is a sophisticated python package
for fitting models with complex parameter correlations
\cite{Buchner2016Ultranest}.  UltraNest implements a variation of
Monte Carlo integration, nested-sampling, where a likelihood contour
is used to update a group of live points chosen from the prior
estimation ($0^{\circ} \leq \theta_k \leq 180^{\circ}$).

The UltraNest software was used to create a set of live points of
different choices of $\theta_1$, $\theta_2$, and $\theta_3$, with each
point being evaluated by its improvement factor ($F(K_l)$).  After
evaluating every live point, the worst results are removed and new
live points are created based on the information provided by the
previous live points.  If there is a correlation between the choice of
angles and $F(K_l)$ then the live points should congregate around a
single (or multiple) choice of angles that will maximise $F(K_l)$ and
therefore minimise the error between our estimate and instantaneous
orientation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results and  Discussion}
\label{sec:Discussion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Asymmetric dimer dynamics}
\label{sec:3.1}

The Brownian OT software was used to simulate the motion of a trapped
dimer ($a_1=1\mu m, a_2=0.5\mu m$) over the first $10$\,seconds of
entering the optical trap.  The initial orientation was assumed as
strictly vertical (in line with the beam propagation direction). The
dimer's position orientation was recorded every $10\,{\rm \mu s}$ for
using as a test dataset for our model.

@@

As can be seen from Figure~\ref{fig:motion}, the dimer undergoes a
full $180^{\circ}$ rotation upon entering the trap. Typically
horizontal alignment of a dimer is unstable and will result in the
particle rotating to align along its vertical axis. It is interesting
to note that the dimer is furthest from the trap centre as it goes
into a horizontal orientation before drawing closer again as it
inverts completely. Further simulations of differently sized dimers
showed similar results, but only when $a_1 \geq 2a_2$. Dimers with
more symmetrical size ratios immediately aligned into a fixed vertical
position.
%
In Vigilante's work with dimers \cite{Vigilante2020Brownian_OT}
simulations of trapped symmetrical dimers was investigated; their
findings showed that the optical torque on the dimer goes to zero
while aligned vertically and is at its maximum in a horizontal
alignment.  Therefore, the inversion of an asymmetric dimer suggests
that if the size difference is significant the optical torque goes is
minimal for a dimer in both horizontal and vertical orientations. Once
we have our experimental set up complete we can confirm this by
trapping an asymmetric dimer and monitoring its orientation. The data
from \figurename{ 2a} was used to test the efficacy of our predictive
model. To visualise how well our model tracks the dimer's orientation
we plot the radial distance between our model's prediction and the
true orientation, and between the best possible orientation and the
true orientation. For a perfect estimation these two plots should
overlap, while we cannot achieve an exact estimation we can optimise
it by adjusting the expected signal error and weighting factor.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Impact of signal error on model predictions}
\label{sec:3.2}

A key assumption of Eq.~\eqref{eq:conditional} is that we assume our
detected light signal will inherently have some degree of noise. This
is the central premise that allows us to form
Eq.~\eqref{eq:conditional}, understanding the limits of acceptable
signal error is necessary for implementing this to experimental work.
To this end we ran our model while varying the value of $\epsilon$.
\figurename{ 3} shows the performance of the method with a selection
of angles $15^{\circ}$, $55^{\circ}$, and $90^{\circ}$ and $\beta$ set
to $1$.  The dotted line indicates the minimum radian distance
($0.137$ radians) between two neighbouring reference orientations, if
we are under this line then we know our model is just off from
selecting the correct orientation

@@

We have developed a method for interpreting the dynamics of a trapped
particle based purely on the light scattering pattern. In theory the
model can be applied to any characteristic that impacts the light
scattering pattern produced by the trapped entity. The MSTM package is
flexible in calculating the light scattering for a variety of
micro-particles; so long as there is a distinguishable difference in
the light scattering pattern we can apply this method to characterise
the particle to some degree of accuracy. This has potential to be
applied to characterise particle size and shape that are changing
while in the optical trap. The authors would like to acknowledge and
thank the support for this research from the funding provided by the
Leverhulme Trust.\\

@@

\newpage
\appendix
\onecolumn
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Appendix}
\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}
\label{sec:App1}
\begin{table}[h]
\begin{center}
\caption{\label{tab:A1}
%
Reference Orientations vector components$^*$}
\begin{tabular}{|c|c|c|c|}
\hline\hline
Reference Orientation & $\hat{\bf n}_{i,\ x}$ &  $\hat{\bf n}_{i,\ y}$ &  $\hat{\bf n}_{i,\ z}$ \\
\hline
$1$ & $ 0.29588$ &  $ 0.29588$ & $ 0.90825$ \\
$2$ & $ 0.90825$ &  $ 0.29588$ & $ 0.29588$ \\
$3$ & $ 0.29588$ &  $ 0.90825$ & $ 0.29588$ \\
$4$ & $1.0000$ &  $0.00000$ & $0.00000$ \\
$5$ & $0.00000$ &  $1.0000$ & $0.00000$ \\
$6$ & $0.00000$ &  $0.00000$ & $1.0000$ \\
$7$ & $ 0.29588$ &  $ 0.29588$ & $-0.90825$ \\
$8$ & $ 0.90825$ &  $ 0.29588$ & $-0.29588$ \\
$9$ & $ 0.29588$ &  $ 0.90825$ & $-0.29588$ \\
$10$ & $0.00000$ &  $0.00000$ & $-1.0000$ \\
$11$ & $ 0.29588$ &  $-0.29588$ & $ 0.90825$ \\
$12$ & $ 0.90825$ &  $-0.29588$ & $ 0.29588$ \\
$13$ & $ 0.29588$ &  $-0.90825$ & $ 0.29588$ \\
$14$ & $0.00000$ &  $-1.0000$ & $0.00000$ \\
$15$ & $ 0.29588$ &  $-0.29588$ & $-0.90825$ \\
$16$ & $ 0.90825$ &  $-0.29588$ & $-0.29588$ \\
$17$ & $ 0.29588$ &  $-0.90825$ & $-0.29588$ \\
$18$ & $-0.29588$ &  $ 0.29588$ & $ 0.90825$ \\
$19$ & $-0.90825$ &  $ 0.29588$ & $ 0.29588$ \\
$20$ & $-0.29588$ &  $ 0.90825$ & $ 0.29588$ \\
$21$ & $-1.0000$ &  $0.00000$ & $0.00000$ \\
$22$ & $-0.29588$ &  $ 0.29588$ & $-0.90825$ \\
$23$ & $-0.90825$ &  $ 0.29588$ & $-0.29588$ \\
$24$ & $-0.29588$ &  $ 0.90825$ & $-0.29588$ \\
$25$ & $-0.29588$ &  $-0.29588$ & $ 0.90825$ \\
$26$ & $-0.90825$ &  $-0.29588$ & $ 0.29588$ \\
$27$ & $-0.29588$ &  $-0.90825$ & $ 0.29588$ \\
$28$ & $-0.29588$ &  $-0.29588$ & $-0.90825$ \\
$28$ & $-0.90825$ &  $-0.29588$ & $-0.29588$ \\
$30$ & $-0.29588$ &  $-0.90825$ & $-0.29588$ \\
\hline\hline
\multicolumn{4}{l}{\small *Orientation vector points from centre of sphere 1 to centre of sphere 2.} \\
		\end{tabular}
	\end{center}
\end{table}
